Causal Impact of Masks, Policies, Behavior on Early Covid-19 Pandemic in the U.S.

### 2020-09-18 tex/covidEffectOfNPI-revision.tex
Added url of git repo to data section.
Fixed typo in acknowledgements.

%% Formatting instructions move this to the end
% \thanks{We are grateful to Daron Acemoglu, V.V. Chari, Raj Chetty,  Christian Hansen, Glenn Ellison, Ivan Fernandez-Val, David Green,  Ido Rosen, Konstantin Sonin, James Stock, Elie Tamer, and Ivan Werning for helpful comments. We also thank Chiyoung Ahn,
% Joshua Catalano,  Jason Chau, Samuel Gyetvay, Sev Chenyu Hou,
% Jordan Hutchings, and Dongxiao Zhang  for excellent research assistance.  We are especially grateful
% to   C. Jessica E. Metcalf and an anonymous referee for detailed and insightful comments,
% which considerable improved the paper. All mistakes are our own. }

@@

\section{Empirical Analysis}
\subsection{Data}

Our baseline measures for daily Covid-19   cases and deaths are from
\href{https://github.com/nytimes/covid-19-data}{The New York Times (NYT)}. When there are missing values in NYT, we use reported cases and deaths from \href{https://github.com/CSSEGISandData/COVID-19}{JHU CSSE}, and then the
\href{https://github.com/COVID19Tracking/covid-tracking-data}{Covid
Tracking Project}.  The number of tests for each state is from  \href{https://github.com/COVID19Tracking/covid-tracking-data}{Covid
 Tracking Project}. As shown in the lower right panel of Figure \ref{fig:casedeathtest} in the appendix, there was a rapid increase in testing in the second half of March and then the
number of tests increased very slowly in each state in April.

@@

We are grateful to Daron Acemoglu, V.V. Chari, Raj Chetty, Christian
Hansen, Glenn Ellison, Ivan Fernandez-Val, David Green, Ido Rosen,
Konstantin Sonin, James Stock, Elie Tamer, and Ivan Werning for
helpful comments. We also thank Chiyoung Ahn, Joshua Catalano, Jason
Chau, Samuel Gyetvay, Sev Chenyu Hou, Jordan Hutchings, and Dongxiao
Zhang for excellent research assistance.  We are especially grateful
to C. Jessica E. Metcalf and an anonymous referee for detailed and
insightful comments, which considerable improved the paper. All
mistakes are our own.

>>>>

%% Formatting instructions move this to the end
% \thanks{We are grateful to Daron Acemoglu, V.V. Chari, Raj Chetty,  Christian Hansen, Glenn Ellison, Ivan Fernandez-Val, David Green,  Ido Rosen, Konstantin Sonin, James Stock, Elie Tamer, and Ivan Werning for helpful comments. We also thank Chiyoung Ahn,
% Joshua Catalano,  Jason Chau, Samuel Gyetvay, Sev Chenyu Hou,
% Jordan Hutchings, and Dongxiao Zhang  for excellent research assistance.  We are especially grateful
% to   C. Jessica E. Metcalf and an anonymous referee for detailed and insightful comments,
% which considerably improved the paper. All mistakes are our own. }

@@

\section{Empirical Analysis}

\subsection{Data}

\footnote{All code is available at \url{https://github.com/ubcecon/covid-impact}.}Our baseline measures for daily Covid-19  cases and deaths are from
\href{https://github.com/nytimes/covid-19-data}{The New York Times (NYT)}. When there are missing values in NYT, we use reported cases and deaths from \href{https://github.com/CSSEGISandData/COVID-19}{JHU CSSE}, and then the
\href{https://github.com/COVID19Tracking/covid-tracking-data}{Covid
Tracking Project}.  The number of tests for each state is from  \href{https://github.com/COVID19Tracking/covid-tracking-data}{Covid
 Tracking Project}. As shown in the lower right panel of Figure \ref{fig:casedeathtest} in the appendix, there was a rapid increase in testing in the second half of March and then the
number of tests increased very slowly in each state in April.

@@

We are grateful to Daron Acemoglu, V.V. Chari, Raj Chetty, Christian
Hansen, Glenn Ellison, Ivan Fernandez-Val, David Green, Ido Rosen,
Konstantin Sonin, James Stock, Elie Tamer, and Ivan Werning for
helpful comments. We also thank Chiyoung Ahn, Joshua Catalano, Jason
Chau, Samuel Gyetvay, Sev Chenyu Hou, Jordan Hutchings, and Dongxiao
Zhang for excellent research assistance.  We are especially grateful
to C. Jessica E. Metcalf and an anonymous referee for detailed and
insightful comments, which considerably improved the paper. All
mistakes are our own.
